\textit{Supplementary materials for:} Fitness tracking reveals task-specific associations between memory, mental health, and exercise

### 2022-07-18 paper/supplement.tex
updated author affiliations

\title{\textit{Supplementary materials for:} Fitness tracking reveals task-specific associations between
  memory, mental health, and exercise}
\author[1, $\star$]{Jeremy R. Manning}
\author[1,2]{Gina M. Notaro}
\author[1]{Esme Chen}
\author[1]{Paxton C. Fitzpatrick}
\affil[1]{Dartmouth College, Hanover, NH}
\affil[2]{Lockheed Martin, Bethesda, MD}
\affil[$\star$]{Address correspondence to jeremy.r.manning@dartmouth.edu}

@@

\begin{sidewaysfigure}[p]
\centering
\includegraphics[width=1\textwidth]{figs/naturalistic_recall_behavior}
\caption{\textbf{Naturalistic recall behavioral results.}
  \textbf{a. Identified topics.}  Applying a topic model to a series
  of sliding windows of the video's transcript~\citep{HeusEtal21}
  revealed a set of 13 unique (non-trivial) topics.  The Panel
  displays the 5 top-weighted words from each topic.  \textbf{b. Topic
  timecourse of the video.}  Each row displays the topic weights for a
single moment of the video.  \textbf{c. Topic correlation matrix.}  The
correlations between the topic vectors for each pair of moments from
the video reveals an event-like block diagonal structure.
\textbf{d. Video topic trajectory.}  The topic video's topic
timecourse (Panel b) has been projected onto 2-dimensions using
Uniform Manifold Approximation and
Projection~\citep[UMAP;][]{McInEtal18}.  Each colored dot reflects an
event, identified by applying a Hidden Markov Model to the video's
topic timecourse~\citep{BaldEtal17, HeusEtal21}.  Red dots denote
earlier timepoints in the video and blue dots denote later
timepoints.  \textbf{e. Immediate recall trajectory.}  The black curve
displays the average
topic timecourse (projected into 2D using UMAP), obtained by applying the topic model shown in Panel A
to the participants' written transcripts from the immediate recall
test.  The arrows denote agreement across participants in the
directions of their topic trajectories, for participants whose
trajectories intersected the corresponding region of topic space.
Blue arrows denote reliable agreement across participants ($p < 0.05$, corrected).
\textbf{f. Delayed recall trajectory.} This panel is in the same
format as Panel e, but displays the trajectory for participants'
delayed recall of the video.  \textbf{g. Immediate recall precision.}  Distribution of
average recall \textit{precision}, across all of the events each
participant recalled during the immediate recall test.  Precision is
defined as the correlation between the topic vector for a given
recalled event and the best-matching (most highly correlated) video
event's topic
vector~\citep{HeusEtal21}.  \textbf{h. Delayed recall precision.}
This panel is in the same format as Panel g, but displays the average
precision values for the delayed memory test.}
\label{fig:nat_behavioral}
\end{sidewaysfigure}

@@

Sleep duration          & Estimated number of hours slept during the prior 24 hour period                                                                                                                      & hours (hr)                               \\

@@

\begin{sidewaysfigure}[p]
\centering
\includegraphics[width=\textwidth]{figs/fitness_scatter_immediate}
\caption{\textbf{Scatterplots of fitness measures versus
    immediate task performance measures.}  The scatterplots of recent
  (Panel a), baselined (Panel b), and static (Panel c) fitness
  measures (Tab.~\ref{tab:abbreviations}) are plotted against 
  participants' performance on each immediate recall test
  (Figs.~\immediateBehavior, \ref{fig:fr_behavioral}, \ref{fig:nat_behavioral}, \ref{fig:vocab_behavioral}, and \ref{fig:spatial_behavioral})}
\label{fig:fitness_scatters_immediate}
\end{sidewaysfigure}

@@

\begin{sidewaysfigure}[p]
\centering
\includegraphics[width=\textwidth]{figs/fitness_scatter_delayed}
\caption{\textbf{Scatterplots of fitness measures versus
    delayed task performance measures.} The scatterplots of recent
  (Panel a), baselined (Panel b), and static (Panel c) fitness
  measures (Tab.~\ref{tab:abbreviations}) are plotted against 
  participants' performance on each delayed recall test
  (Figs.~\delayedBehavior, \ref{fig:fr_behavioral},
  \ref{fig:nat_behavioral}, and \ref{fig:vocab_behavioral})}
\label{fig:fitness_scatters_delayed}
\end{sidewaysfigure}

@@

  \clearpage
  \newpage
\bibliographystyle{apa}
\bibliography{/Users/jmanning/CDL-bibliography/cdl}
\end{document}

>>>>

\title{\textit{Supplementary materials for:} Fitness tracking reveals task-specific associations between
  memory, mental health, and exercise}
\author[1, $\star$]{Jeremy R. Manning}
\author[1]{Gina M. Notaro}
\author[1]{Esme Chen}
\author[1]{Paxton C. Fitzpatrick}
\affil[1]{Dartmouth College, Hanover, NH}
\affil[$\star$]{Address correspondence to jeremy.r.manning@dartmouth.edu}

@@

\begin{sidewaysfigure}[p]
\centering
\includegraphics[width=1\textwidth]{figs/naturalistic_recall_behavior}
\caption{\textbf{Naturalistic recall behavioral results.}
  \textbf{a. Identified topics.}  Applying a topic model to a series
  of sliding windows of the video's transcript~\citep{HeusEtal21}
  revealed a set of 13 unique (non-trivial) topics.  The Panel
  displays the 5 top-weighted words from each topic.  \textbf{b. Topic
  timecourse of the video.}  Each row displays the topic weights for a
single moment of the video.  \textbf{c. Topic correlation matrix.}  The
correlations between the topic vectors for each pair of moments from
the video reveals an event-like block diagonal structure.
\textbf{d. Video topic trajectory.}  The topic video's topic
timecourse (Panel b) has been projected onto 2-dimensions using
Uniform Manifold Approximation and
Projection~\citep[UMAP;][]{McInEtal18}.  Each colored dot reflects an
event, identified by applying a Hidden Markov Model to the video's
topic timecourse~\citep{BaldEtal17, HeusEtal21}.  Red dots denote
earlier timepoints in the video and blue dots denote later
timepoints.  \textbf{e. Immediate recall trajectory.}  The black curve
displays the average
topic timecourse (projected into 2D using UMAP), obtained by applying the topic model shown in Panel A
to the participants' written transcripts from the immediate recall
test.  The arrows denote agreement across participants in the
directions of their topic trajectories, for participants whose
trajectories intersected the corresponding region of topic space.
Blue arrows denote reliable agreement across participants ($p < 0.05$, corrected).
\textbf{f. Delayed recall trajectory.} This panel is in the same
format as Panel e, but displays the trajectory for participants'
delayed recall of the video.  \textbf{g. Immediate recall precision.}  Distribution of
average recall \textit{precision}, across all the events each
participant recalled during the immediate recall test.  Precision is
defined as the correlation between the topic vector for a given
recalled event and the best-matching (most highly correlated) video
event's topic
vector~\citep{HeusEtal21}.  \textbf{h. Delayed recall precision.}
This panel is in the same format as Panel g, but displays the average
precision values for the delayed memory test.}
\label{fig:nat_behavioral}
\end{sidewaysfigure}

@@

Sleep duration          & Estimated number of hours slept during the prior 24-hour period                                                                                                                      & hours (hr)                               \\

@@

\begin{sidewaysfigure}[p]
\centering
\includegraphics[width=\textwidth]{figs/fitness_scatter_immediate}
\caption{\textbf{Scatter plots of fitness measures versus
    immediate task performance measures.}  The scatter plots of recent
  (Panel a), baselined (Panel b), and static (Panel c) fitness
  measures (Tab.~\ref{tab:abbreviations}) are plotted against 
  participants' performance on each immediate recall test
  (Figs.~\immediateBehavior, \ref{fig:fr_behavioral}, \ref{fig:nat_behavioral}, \ref{fig:vocab_behavioral}, and \ref{fig:spatial_behavioral})}
\label{fig:fitness_scatters_immediate}
\end{sidewaysfigure}

@@

\begin{sidewaysfigure}[p]
\centering
\includegraphics[width=\textwidth]{figs/fitness_scatter_delayed}
\caption{\textbf{Scatter plots of fitness measures versus
    delayed task performance measures.} The scatter plots of recent
  (Panel a), baselined (Panel b), and static (Panel c) fitness
  measures (Tab.~\ref{tab:abbreviations}) are plotted against 
  participants' performance on each delayed recall test
  (Figs.~\delayedBehavior, \ref{fig:fr_behavioral},
  \ref{fig:nat_behavioral}, and \ref{fig:vocab_behavioral})}
\label{fig:fitness_scatters_delayed}
\end{sidewaysfigure}

@@

  \clearpage
  \newpage
\bibliographystyle{apa}
\bibliography{/home/jeremy/CDL-bibliography/cdl}
\end{document}
